%-------------------------
% Resume in Latex
% Author : Timothy Kilmer
% Inspirations : Aras Güngöre -> https://github.com/arasgungore
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{xifthen}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage[utf8]{inputenc}

\titleformat{\section}
	{\vspace{-4pt}\scshape\raggedright\large}
	{}
	{0em}
	{}
	[\titlerule \vspace{-5pt}]


\def\name{Timothy W. Kilmer Jr.}
\def\email{timothywkilmer@gmail.com}

\def\address{3935 Colechester Mtn Rd. Walton, NY 13856}
\def\phoneNumber{(607) 643-6631}

%custom commands for document 




\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #3 \\
		\textit{\small#2} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeItem}[1]{ \item\small{ { #1 \vspace{ -2pt } } } } 
\newcommand{\skillItem}[2]{\item\textit{#1} : #2\vspace{-5pt}}

%\newcommand{\isResumeItemEmpty}[1]

%job specific items
\newcommand{\jobItem}[9]{
	\resumeSubheading{#1}{#2}{#3}{#4}
		\resumeItemListStart
			\ifthenelse{\isempty{#5}} {} {\resumeItem{ #5}}
			\ifthenelse{\isempty{#6}} {} {\resumeItem{ #6}}
			\ifthenelse{\isempty{#7}} {} {\resumeItem{ #7}}
			\ifthenelse{\isempty{#8}} {} {\resumeItem{ #8}}
			\ifthenelse{\isempty{#9}} {} {\resumeItem{ #9}}
		\resumeItemListEnd
	}

\begin{document}
	\begin{center}
		{\LARGE \textbf{\name}} \\ \vspace{2pt}
		{\small \address}\\ 
		{\small \email \space \phoneNumber} \\ \vspace{2pt}		
	\end{center}
	
	%-----------EDUCATION-----------
	\section{EDUCATION}
		\resumeSubHeadingListStart
			\item \textbf{Clarkson University} \hfill Potsdam, NY  \\
			\textit{Bachelor of Science in Electrical Engineering, Minor in Mathematics; Dean’s list, GPA 3.5 \hfill Fall 2016 - 2018}\\
		 	\item \textbf{State University of New York (SUNY) at Oneonta} \hfill Oneonta, NY  \\
		 	\textit{Bachelor of Science in Physics, 3+2 Engineering program; GPA 3.75 \hfill Fall 2013 - 2018}\\
		\resumeItemListEnd

	%-----------Skills /Summary-----------
	\section{TECHNICAL SUMMARY}
		\resumeSubHeadingListStart
			\skillItem{Programming Languages}{C, C++, Python, VHDL, Verilog}
			\skillItem{Drivers}{Ethernet, UART, I2C, SPI, ADC, DAC, Dataflash, Flash, GPIO}
			\skillItem{Protocols}{TCP/IP, DHCP, MQTT, BSP Sockets, PMBus/SMBus, YModem, XModem, OPC-UA}
			\skillItem{Lab / Debug Tools}{Oscilloscope, Function Generator, DC/AC Power Supplies, In circuit emulators (Jlink), GDB}
			\skillItem{Development Tools}{E2 Studio, Eclipse, GCC, IAR, Wireshark, MATLAB, Simulink, Altera Quartus II, Xilinx Vivado}
			\skillItem{CI/CD Tools}{Git, Gitlab, Jenkins, Docker, KVM}
			\skillItem{Host / Target OS}{Windows, Linux, RTOS (ThreadX)}
			\skillItem{Hardware Skills}{Reading Schematics, Digital Circuit Design, Controls Design, Soldering}
			\skillItem{Documentation Tools}{Microsoft Office (Word, Excel, and Powerpoint), Jupyter Notebooks, \LaTeX}
		\resumeItemListEnd

	%-----------EXPERIENCE-----------
	\section{PROFESSIONAL EXPERIENCE}
		\resumeSubHeadingListStart
			%ask Ken if i am allowed to talk about projects I have worked on?  or If I have to talk about vaigue ideas ?
			\jobItem{International Business Machines (IBM)}{Firmware Design Engineer}{Poughkeepsie NY}{June 2018-present}
			{Implemented feature to enable customers to configure and fetch both system and application configuration using DHCP options.}
			{Developed and designed MQTT interface for firmware to communicate with system tools over MQTT for cloud administration of devices in the field. }
			{Debuged and developed applications that have communicated over I2C,UART,SPI, program and dataflash, and TCP/IP.}
			{Worked on code to update firmware and downstream devices over the network.}
			{}
			
	
			\jobItem{LC Drives}{Electrical/Controls Engineer Intern}{Potsdam NY}{May 2017-September 2017}
			{Designed controls for automation using DipTrace schematic tool.}
			{Integrated git and python for development of automation software.}
			{Designed instrumentation controls to meet the national electric code by NFPA and project requirements.}
			{}
			{}
	
			\jobItem{Hack Potsdam Hack-a-thon at Clarkson University}{Participant}{Potsdam NY}{March 2017}
			{Implemented CPU in VHDL hardware description language to design the ALU and VHDL code debugging. }
			{Worked with Git and Git-hub for version control of group code. }
			{}
			{}
			{}

			\jobItem{Graphene Structure Simulation National Science Foundation}{Intern}{Troy, NY}{June - August 2016}
			{Prepared scripts for handling input and to run files used in Density Functional Theory (DFT) calculations.}
			{Rapid 3D prototyping of molecular structures for kinetic learning.}
			{Basic introduction to Linux terminal and ssh file transfer from server and home computer.}
			{ }
			{ }
				
			\jobItem{Energy Harvesting/MEMS SUNY Research Foundation}{Intern}{Vestal, NY}{May - July 2015}
			{Interned as a Lab Assistant in the research and fabrication of MEMS and energy harvesting devices.}
			{Oversaw design of photomasks, photolithography printing and development, and Reactive Ion etching. }
			{Worked on restoration of MEMS devices and proper clean room procedures using manual wire-binding machine. }
			{ }
			{ }
	
		\resumeItemListEnd
	

	%-----------leadership-----------
	\section{Projects}
		\resumeSubHeadingListStart
			\resumeSubSubheading{Homelab}{idk}
			\resumeSubSubheading{Sit Stand Arduino Mod}{idk}
			\resumeSubSubheading{FPGA based Audio Multiplex/Mixer}{idk}
		\resumeItemListEnd
		
%-----------leadership-----------
	\section{LEADERSHIP EXPERIENCE}
		\resumeSubHeadingListStart
			\jobItem{SUNY Oneonta}{Peer and Group Tutor}{Oneonta, NY}{February 2015 - May 2016}
				{Guided students in vector calculus in a one-on-one environment}
				{Led student peers in general college physics for walk-in tutoring}
				{}
				{}
				{}
		
			\jobItem{Oneonta Tech. and Engn. Club SUNY Oneonta}{Manager}{Oneonta, NY}{October 2015 - May 2016}
				{ Supervised club and shop activities relating to electronics, wood working, and project design.}
				{ Kept innovatory of tools, equipment, and supplies}
				{}
				{}
				{}
			
			\jobItem{Physics and Astronomy Club}{Public Relations and Treasurer}{ Oneonta, NY}{September 2014 - May 2016}
				{Public Relations- Held communication between public and club advertising events and activities.}
				{Treasurer- Responsible for the management of club expenses and budget of \$500 for events and activities.}
				{Coordinated club events and activities with President and Student Union}
				{}
				{}		
				
			\jobItem{Boy Scouts of America Troop 45}{Eagle Scout Award}{Walton, NY}{April 2012}
				{Led and planned project that entailed the construction of record boards for local high school track teams.}
				{Organized volunteers in community in the fund raising, construction, and instillation of the record boards.}
				{Complied with constraints set by the high school, Boy Scouts of America, and State Code.}
				{Documented project plans so they can be reproduced for anyone that wanted to reproduce my project.}	
				{}		
		\resumeItemListEnd
		
		
	\section{RELEVANT AFFILIATIONS}
		\resumeSubHeadingListStart
			\jobItem{Clarkson Open Source Institute (COSI)}{Clarkson University}{Potsdam, NY}{2016 -May 2018}
			{Robotics using Robot Operating System (ROS)}{}{}{}{}
		\resumeItemListEnd
	
\end{document}}